---
title: "AN588_Week3_dippelm"
author: "Max Dippel"
date: "9/21/2021"
output: html_document
---

#Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

library(manipulate)
library(ggplot2)

```{r}

# What is the probability that she will hear more than 8 calls during any given session?
1 - ppois(q = 8, lambda = 15)

```


```{r}

# What is the probability that she will hear no calls in a session?
ppois(q = 0, lambda = 15)

```


```{r}

# What is the probability that she will hear exactly 3 calls in a session?
dpois(x = 3, lambda = 15)

```


```{r}

# Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
x <- 0:30
l <- 15
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability Mass Function")

```


```{r}
# Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
n.Sat <- 104
Sat <- function(x) {
    dpois(x = 0:30, lambda = 15)
}

two.year.Sat <- Sat(n.Sat)
hist(two.year.Sat, probability = TRUE)

n.Sat <- 104
Sat <- function(x) {
    rpois(x = 104, lambda = 15)
}
two.year.Sat <- Sat(n.Sat)
hist(two.year.Sat, probability = TRUE)


# Cannot figure out how to get results 
# dpois() outputs probabilities not number of calls
```


```{r}

# Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

Titi.plot <- rpois(n = 104, lambda = 15)
hist(Titi.plot) 
?xlim
# Cannot figure out xlim
# Also this is a way to do what was asked but I am not using code from the last question
```










