---
title: "AN588_Week3_dippelm"
author: "Max Dippel"
date: "9/21/2021"
output: html_document
---

#Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

library(manipulate)
library(ggplot2)

```{r}

# What is the probability that she will hear more than 8 calls during any given session?
1 - ppois(q = 8, lambda = 15)

```

*you can also set lower = false so that the function gives you the probability of x being greater than 8 instead of lower than 8 which is the default for ppois. -Mel*

```{r}

# What is the probability that she will hear no calls in a session?
ppois(q = 0, lambda = 15)

```


```{r}

# What is the probability that she will hear exactly 3 calls in a session?
dpois(x = 3, lambda = 15)

```


```{r}

# Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
x <- 0:30
l <- 15
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability Mass Function")

```


```{r}
# Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

calls <- data.frame(data = rpois(n = 104, lambda = 15))

hist(calls$data)

```

*No need to put it in a data frame here! The hist() function can take an object that is the product of rpois() (like you do below). Also, don't forget to set your hist() parameters (x and y labels, limits, breaks, etc), you will be able to look at it with more detail. -mel* 
```{r}

# Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above? 

Titi.plot <- rpois(n = 104, lambda = 15)
hist(Titi.plot, xlim = c(0,30)) 

```

*dont forget to answer the questions with the code, and annotate! -Mel*
